US General Society Survey Analysis

### 2024-03-17 paper/paper.qmd
minor edits
Update paper.qmd

## Model 2
In this model, we conduct an examination of the relationship between voters' birth year and their gender for the 2016 and 2020 Presidential elections. This analysis is visualized by plotting a histogram that separate female voters on the left and male voters on the right, with voters' birth years measured along the x-axis, which ranges from 1925 to 2002. The y-axis quantifies the voter turnout for the year. For clarity ad symbolic representation, the colour blue was chosen to represent the Democratic candidates --Hillary Clinton for the 2016 election, and Joe Biden for the 2020 election, while red was chosen to the Represent the Republican candidate, Donald Trump, who sought the presidency in both terms. @fig-genderyr2016 present the distribution of votes in 2016, and @fig-genderyr2020 presents the data from the 2020 election.

@@

kables(list(votes_2020_f, votes_2020_m))
#If the ratio is greater than 1, it means that within the group, Biden has more votes than Trump
#if the ratio is less than 1, Trump has more votes within the group
```

@@

kables(list(votes_2020_f, votes_2020_m))
#If the ratio is greater than 1, it means that within the group, Biden has more votes than Trump
#if the ratio is less than 1, Trump has more votes within the group
```

@@

## Model 3

@@

## Dissecting Age Related Demographics

@@

>>>>

## Comparing 2016 and 2020 votes based on birth year and gender
In this model, we conduct an examination of the relationship between voters' birth year and their gender for the 2016 and 2020 Presidential elections. This analysis is visualized by plotting a histogram that separate female voters on the left and male voters on the right, with voters' birth years measured along the x-axis, which ranges from 1925 to 2002. The y-axis quantifies the voter turnout for the year. For clarity ad symbolic representation, the colour blue was chosen to represent the Democratic candidates --Hillary Clinton for the 2016 election, and Joe Biden for the 2020 election, while red was chosen to the Represent the Republican candidate, Donald Trump, who sought the presidency in both terms. @fig-genderyr2016 present the distribution of votes in 2016, and @fig-genderyr2020 presents the data from the 2020 election.

@@

votes_2020_f
votes_2020_m
#If the ratio is greater than 1, it means that within the group, Biden has more votes than Trump
#if the ratio is less than 1, Trump has more votes within the group
```

@@

votes_2020_f
votes_2020_m
```

@@

## Predicitng 2020 votes based off regression variables

@@

## Dissecting Age Related Voting Patterns

@@

## Comparing 2016 and 2020 votes votes based on birth year and gender

Our analysis displayed interesting results when when examining gender-based voting behaviors the from 2016 and 2020 US Presidential election votes in @fig-genderyr2016 and @fig-genderyr2020. We notice from the graphs and in @tbl-ratio2020 most votes were for the Republican Party in 2016, while most votes for the Democratic Party in 2020. Female voters have a higher ratio of Democratic voters to Republican voters in both years. In contrast, the distribution of male votes between the two parties was more evenly balanced. The most interesting and abstract result is that the votes are reversed in 2016 compared to 2020. There can be many explanations for this reverse, including that Americans were not satisfied with the Republican Presidency from 2016 to 2020. Further research should be done into the reason why there is a higher ratio of Democratic to Republican female voters compared to male voters.

## Third discussion point
